# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
First, I loaded the data without any preprocessing.

```{r, cache=TRUE}
dt<-read.csv('activity.csv')

```


## What is mean total number of steps taken per day?
Here's a histogram of the total number of steps taken each day.

```{r, cache=TRUE}
hist(dt$steps, xlab="", main="Total number of steps taken each day")
meanStep<-mean(dt$steps, na.rm=TRUE)
medianStep<-median(dt$steps, na.rm=TRUE)
```

The mean and median total number of steps taken per day are `r meanStep` and `r medianStep`, respectively.

## What is the average daily activity pattern?

Here's a time series plot of the number of steps, averaged across all days, against the 5-minute intervals.

```{r, cache=TRUE}
library(plyr)
dt.average<-ddply(dt, .(interval), summarise, steps=mean(steps, na.rm=TRUE))
with(dt.average, plot(interval, steps, type="l"))
maxStepsIndex<-with(dt.average, which(steps==max(steps)))
maxStepsInterval<-dt.average[maxStepsIndex, "interval"]
```

On average across all the days, the 5-minute interval from `r maxStepsInterval` to `r maxStepsInterval+5` contains the maximum number of steps.

## Imputing missing values
Here I replaced the missing values with the mean for that 5-minute interval calculated before.

```{r, cache=TRUE}
# Total number of missing value:
totalNA<-sum(is.na(dt$steps))

# Replace the NA's 
dt.replaced<-dt
NAindex<-which(is.na(dt.replaced$steps))
dt.replaced[NAindex,]$steps<-dt.average[(dt.replaced[NAindex,"interval"]/5+1),"steps"]

hist(dt.replaced$steps, xlab="", main="Total number of steps taken each day (NA's replaced)")
meanStepNew<-mean(dt.replaced$steps, na.rm=TRUE)
medianStepNew<-median(dt.replaced$steps, na.rm=TRUE)
```

The total number of NA's is `r totalNA`. After replacing the NA's, the new mean and median total number of steps taken per day are `r meanStepNew` and `r medianStepNew`, respectively. Replacing the NA's does not seem to have a big impact.


## Are there differences in activity patterns between weekdays and weekends?


```{r}
dt.replaced$date<-as.Date(dt.replaced$date)
dt.replaced$weekday<-as.factor(weekdays(dt.replaced$date))
dt.replaced$index<-"weekday"
dt.replaced[dt.replaced$weekday=="Saturday"|dt.replaced$weekday=="Sunday","index"]<-"weekend"
dt.replaced$index<-as.factor(dt.replaced$index)
library(plyr)
dt.replaced.average<-ddply(dt.replaced, .(interval, index), summarise, steps=mean(steps, na.rm=TRUE))
library(lattice)
xyplot(steps~interval|index, data=dt.replaced.average, type="l", layout=c(1,2))

```

There does seem to be some slight difference between weekend and weekdays.